Temporal Transfer Learning with ``HERE'':\\ Local Policy Generation (in Near Linear Time)

### 2015-04-29 manuscript.tex
Updates from ShareLaTeX

\begin{document}
  \title{``Don't tell me what it is, tell me what to do'':\\Instance-Based Planning for Actionable Analytics}

  % make the title area
  \maketitle

  \begin{abstract}

  \end{abstract}
  \begin{IEEEkeywords}
    defect prediction, CART
  \end{IEEEkeywords}

\section{Introduction}
{\bf RQ1: Can Instance-based Learning techniques be used to create Planning tools that can better analyse software defect?}

@@

\begin{figure*}[htbp!]
  \renewcommand{\baselinestretch}{0.8}\begin{center}
    {\scriptsize
      \begin{tabular}{c|l|p{4.7in}}
        amc & average method complexity & e.g. number of JAVA byte codes\\\hline
        avg\_cc & average McCabe & average McCabe's cyclomatic complexity seen
        in class\\\hline
        ca & afferent couplings & how many other classes use the specific
        class. \\\hline
class. \\\hline
        cam & cohesion amongst classes & summation of number of different
        types of method parameters in every method divided by a multiplication
        of number of different method parameter types in whole class and
        number of methods. \\\hline
        cbm &coupling between methods &  total number of new/redefined methods
        to which all the inherited methods are coupled\\\hline
        cbo & coupling between objects & increased when the methods of one
        class access services of another.\\\hline
        ce & efferent couplings & how many other classes is used by the
        specific class. \\\hline
        dam & data access & ratio of the number of private (protected)
        attributes to the total number of attributes\\\hline
        dit & depth of inheritance tree &\\\hline
        ic & inheritance coupling &  number of parent classes to which a given
        class is coupled (includes counts of methods and variables inherited)
        \\\hline
        lcom & lack of cohesion in methods &number of pairs of methods that do
        not share a reference to an instance variable.\\\hline
        locm3 & another lack of cohesion measure & if $m,a$ are  the number of
        $methods,attributes$
        in a class number and $\mu(a)$  is the number of methods accessing an
        attribute, 
        then
        $lcom3=((\frac{1}{a} \sum_j^a \mu(a_j)) - m)/ (1-m)$.
        \\\hline
        loc & lines of code &\\\hline
        max\_cc & maximum McCabe & maximum McCabe's cyclomatic complexity seen
        in class\\\hline
        mfa & functional abstraction & number of methods inherited by a class
        plus number of methods accessible by member methods of the
        class\\\hline
        moa &  aggregation &  count of the number of data declarations (class
        fields) whose types are user defined classes\\\hline
        noc &  number of children &\\\hline
        npm & number of public methods & \\\hline
        rfc & response for a class &number of  methods invoked in response to
        a message to the object.\\\hline
        wmc & weighted methods per class &\\\hline
        \rowcolor{lightgray}
        defect & defect & Boolean: where defects found in post-release bug-tracking systems.
      \end{tabular}
    }
  \end{center}
  \caption{OO measures used in our defect data sets.  Last line is
    the dependent attribute (whether a defect is reported to  a
    post-release bug-tracking system).}\label{fig:ck}
\end{figure*}

@@

\begin{figure}[tbp!]
% \subfloat[\label{oracle}]{\includegraphics[width=\linewidth]{./_figs/Oracle}}\\
\includegraphics[width=\linewidth]{./_figs/WHAT}
\caption{Experimental Rig}
\label{fig:rig}

%   \subfloat[Experimental Rig for Defect Prediction]{  \includegraphics[width=\linewidth]{./_figs/WHAT}
%   \label{fig:rig2}}

@@

\noindent\begin{minipage}{0.5\textwidth}
  {\scriptsize \textbf{Ant}\\}
  {\scriptsize  \begin{tabular}{{l@{~~~~}l@{~~~~}r@{~~~~}r@{~~~~}c}}
      \arrayrulecolor{darkgray}
      \rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\\hline
  1 & ant,  0.25,  weight &    -0.33  &  0.05 & \quart{1}{5}{3}{149}\\
  1 &   ant,  0.25 &    -0.31  &  0.06 & \quart{2}{6}{5}{149}\\
  1 &    ant,  0.5 &    -0.28  &  0.15 & \quart{1}{16}{8}{149}\\
\hline  2 & ant,  0.5,  weight &    -0.26  &  0.19 & \quart{0}{20}{10}{149}\\
  2 & ant,  0.5,  weight,  iP= 50\\% &    -0.26  &  0.11 & \quart{5}{12}{10}{149}\\
  2 & ant,  0.75,  weight &    -0.25  &  0.3 & \quart{0}{32}{12}{149}\\
  2 &   ant,  0.75 &    -0.23  &  0.23 & \quart{1}{25}{14}{149}\\
  2 & ant,  0.25,  weight,  iP= 50\\% &    -0.22  &  0.08 & \quart{8}{9}{15}{149}\\
  2 & ant,  0.75,  weight,  iP= 50\\% &    -0.21  &  0.13 & \quart{8}{15}{16}{149}\\
\hline  3 &   ant,  Base &    -0.13  &  0.03 & \quart{24}{3}{25}{149}\\
\hline \end{tabular}}
\end{minipage}
\noindent\begin{minipage}{0.5\textwidth}
  \flushleft
  {\scriptsize \textbf{Camel}\\}
{\scriptsize  \begin{tabular}{{l@{~~~~}l@{~~~~}r@{~~~~}r@{~~~~}c}}
\arrayrulecolor{darkgray}
\rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\\hline
  1 & camel_0.75_w_iP(50\%) &    -0.45  &  0.17 & \quart{0}{21}{8}{189}\\
\hline  2 &   camel_0.75 &    -0.39  &  0.21 & \quart{8}{26}{16}{189}\\
  2 & camel_0.75_w &    -0.37  &  0.19 & \quart{9}{24}{18}{189}\\
\hline  3 & camel_0.5_w_iP(50\%) &    -0.28  &  0.13 & \quart{19}{17}{29}{189}\\
\hline  4 &  camel_0.5_w &    -0.26  &  0.1 & \quart{27}{12}{32}{189}\\
  4 &    camel_0.5 &    -0.24  &  0.1 & \quart{29}{13}{34}{189}\\
\hline  5 & camel_0.25_w_iP(50\%) &    -0.22  &  0.07 & \quart{33}{9}{37}{189}\\
\hline  6 &   camel_0.25 &    -0.17  &  0.08 & \quart{39}{10}{43}{189}\\
  6 & camel_0.25_w &    -0.17  &  0.06 & \quart{38}{8}{43}{189}\\
  6 &   camel_Base &    -0.16  &  0.02 & \quart{43}{3}{44}{189}\\
\hline \end{tabular}}
\end{minipage}

\noindent\begin{minipage}{0.5\textwidth}
  \flushleft
  {\scriptsize \textbf{Ivy}\\[-0.05cm]}
{\scriptsize  \begin{tabular}{{l@{~~~~}l@{~~~~}r@{~~~~}r@{~~~~}c}}
\arrayrulecolor{darkgray}
\rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\\hline
  1 &     ivy_0.75 &    -0.62  &  0.05 & \quart{0}{4}{1}{141}\\
  1 &   ivy_0.75_w &    -0.61  &  0.09 & \quart{0}{7}{2}{141}\\
\hline  2 &      ivy_0.5 &    -0.56  &  0.09 & \quart{4}{8}{6}{141}\\
  2 &    ivy_0.5_w &    -0.53  &  0.12 & \quart{4}{10}{9}{141}\\
\hline  3 &   ivy_0.25_w &    -0.41  &  0.06 & \quart{17}{5}{19}{141}\\
  3 &     ivy_0.25 &    -0.39  &  0.06 & \quart{18}{6}{21}{141}\\
\hline  4 & ivy_0.75_w_iP(50\%) &    -0.27  &  0.14 & \quart{27}{12}{31}{141}\\
\hline  5 & ivy_0.5_w_iP(50\%) &    -0.18  &  0.06 & \quart{35}{5}{39}{141}\\
\hline  6 & ivy_0.25_w_iP(50\%) &    -0.12  &  0.04 & \quart{42}{3}{44}{141}\\
\hline  7 &     ivy_Base &    -0.06  &  0.0 & \quart{49}{0}{49}{141}\\
\hline \end{tabular}}
\end{minipage}
\noindent\begin{minipage}{0.5\textwidth}
  \flushleft
  {\scriptsize \textbf{Jedit}\\}
  {\scriptsize  \begin{tabular}{{l@{~~~~}l@{~~~~}r@{~~~~}r@{~~~~}c}}
\arrayrulecolor{darkgray}
\rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\\hline
  1 &   jedit_0.75 &    -0.55  &  0.19 & \quart{2}{17}{6}{142}\\
  1 & jedit_0.75_w &    -0.55  &  0.35 & \quart{0}{30}{6}{142}\\
\hline  2 &    jedit_0.5 &    -0.34  &  0.19 & \quart{14}{16}{24}{142}\\
  2 &  jedit_0.5_w &    -0.31  &  0.08 & \quart{23}{7}{27}{142}\\
  2 & jedit_0.75_w_iP(50\%) &    -0.32  &  0.17 & \quart{21}{14}{26}{142}\\
\hline  3 & jedit_0.25_w &    -0.21  &  0.1 & \quart{33}{9}{35}{142}\\
  3 &   jedit_0.25 &    -0.2  &  0.07 & \quart{32}{6}{36}{142}\\
\hline  4 & jedit_0.5_w_iP(50\%) &    -0.16  &  0.11 & \quart{37}{10}{40}{142}\\
\hline  5 & jedit_0.25_w_iP(50\%) &    -0.11  &  0.06 & \quart{42}{6}{44}{142}\\
\hline  6 &   jedit_Base &    -0.05  &  0.0 & \quart{49}{0}{49}{142}\\
\hline \end{tabular}}
\end{minipage}

\noindent\begin{minipage}{0.5\textwidth}
  \flushleft
  {\scriptsize \textbf{Log4j}\\}
  {\scriptsize  \begin{tabular}{{l@{~~~~}l@{~~~~}r@{~~~~}r@{~~~~}c}}
\arrayrulecolor{darkgray}
\rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\\hline
  1 &   log4j_0.75 &    -0.19  &  0.2 & \quart{0}{41}{24}{272}\\
  1 & log4j_0.75_w &    -0.15  &  0.16 & \quart{6}{33}{33}{272}\\
  1 & log4j_0.75_w_iP(50\%) &    -0.15  &  0.05 & \quart{29}{10}{33}{272}\\
  1 &    log4j_0.5 &    -0.15  &  0.09 & \quart{27}{18}{33}{272}\\
\hline  2 &   log4j_0.25 &    -0.12  &  0.07 & \quart{35}{14}{39}{272}\\
  2 &   log4j_Base &    -0.11  &  0.04 & \quart{41}{8}{41}{272}\\
  2 & log4j_0.25_w &    -0.1  &  0.03 & \quart{39}{6}{43}{272}\\
  2 &  log4j_0.5_w &    -0.1  &  0.13 & \quart{22}{27}{43}{272}\\
  2 & log4j_0.25_w_iP(50\%) &    -0.09  &  0.04 & \quart{39}{8}{45}{272}\\
  2 & log4j_0.5_w_iP(50\%) &    -0.09  &  0.05 & \quart{39}{10}{45}{272}\\
\hline \end{tabular}}
\end{minipage}
\noindent\begin{minipage}{0.5\textwidth}
  \flushleft
  {\scriptsize \textbf{Lucene}\\}
  {\scriptsize  \begin{tabular}{{l@{~~~~}l@{~~~~}r@{~~~~}r@{~~~~}c}}
\arrayrulecolor{darkgray}
\rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\\hline
  1 & lucene_0.75_w_iP(50\%) &    -0.27  &  0.16 & \quart{0}{24}{10}{209}\\
  1 &  lucene_0.75 &    -0.25  &  0.1 & \quart{6}{15}{14}{209}\\
  1 & lucene_0.75_w &    -0.22  &  0.14 & \quart{6}{22}{18}{209}\\
\hline  2 & lucene_0.5_w_iP(50\%) &    -0.18  &  0.09 & \quart{15}{14}{24}{209}\\
\hline  3 & lucene_0.5_w &    -0.11  &  0.08 & \quart{29}{13}{35}{209}\\
\hline  4 &  lucene_Base &    -0.1  &  0.01 & \quart{37}{2}{37}{209}\\
  4 &   lucene_0.5 &    -0.09  &  0.07 & \quart{32}{11}{39}{209}\\
  4 & lucene_0.25_w_iP(50\%) &    -0.09  &  0.03 & \quart{37}{5}{39}{209}\\
\hline  5 &  lucene_0.25 &    -0.05  &  0.04 & \quart{42}{6}{45}{209}\\
  5 & lucene_0.25_w &    -0.03  &  0.03 & \quart{45}{4}{48}{209}\\
\hline \end{tabular}}
\end{minipage}

\noindent\begin{minipage}{0.5\textwidth}
  \flushleft
  {\scriptsize \textbf{Poi}\\}
  {\scriptsize  \begin{tabular}{{l@{~~~~}l@{~~~~}r@{~~~~}r@{~~~~}c}}
      \arrayrulecolor{darkgray}
\rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\\hline
  1 &   poi_0.75_w &    -0.59  &  0.36 & \quart{0}{26}{9}{123}\\
  1 &      poi_0.5 &    -0.5  &  0.28 & \quart{12}{20}{16}{123}\\
  1 &     poi_0.75 &    -0.5  &  0.47 & \quart{0}{33}{16}{123}\\
\hline  2 &    poi_0.5_w &    -0.37  &  0.51 & \quart{4}{37}{25}{123}\\
  2 & poi_0.75_w_iP(50\%) &    -0.34  &  0.41 & \quart{15}{29}{27}{123}\\
\hline  3 &   poi_0.25_w &    -0.25  &  0.31 & \quart{23}{22}{34}{123}\\
  3 &     poi_0.25 &    -0.23  &  0.29 & \quart{24}{20}{35}{123}\\
\hline  4 & poi_0.5_w_iP(50\%) &    -0.11  &  0.12 & \quart{39}{9}{44}{123}\\
  4 &     poi_Base &    -0.09  &  0.06 & \quart{43}{4}{45}{123}\\
  4 & poi_0.25_w_iP(50\%) &    -0.08  &  0.15 & \quart{39}{10}{46}{123}\\
\hline \end{tabular}}
\end{minipage}
\noindent\begin{minipage}{0.5\textwidth}
  \flushleft
  {\scriptsize \textbf{Synapse}\\}
  {\scriptsize  \begin{tabular}{{l@{~~~~}l@{~~~~}r@{~~~~}r@{~~~~}c}}
\arrayrulecolor{darkgray}
\rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\\hline
  1 & Base &    0.15  &  0.0 & \quart{1}{0}{1}{44}\\
  1 & 0.5, weighting,  iP=50\% &    0.15  &  0.08 & \quart{1}{4}{1}{44}\\
  1 & 0.25, weighting,  iP=50\% &    0.17  &  0.08 & \quart{0}{4}{2}{44}\\
\hline  2 & 0.75, weighting,  iP=50\% &    0.21  &  0.08 & \quart{1}{4}{4}{44}\\
  2 & 0.25 &    0.23  &  0.18 & \quart{2}{9}{5}{44}\\
  2 & 0.25, weighting&    0.23  &  0.11 & \quart{2}{5}{5}{44}\\
\hline  3 & 0.5, weighting&    0.38  &  0.19 & \quart{7}{10}{12}{44}\\
  3 &  0.5 &    0.42  &  0.27 & \quart{6}{14}{14}{44}\\
\hline  4 & 0.75 &    0.5  &  0.39 & \quart{12}{20}{19}{44}\\
  4 & 0.75, weighting&    0.56  &  0.25 & \quart{17}{12}{22}{44}\\
\hline \end{tabular}}
\end{minipage}

>>>>

\begin{document}
  \title{Temporal Transfer Learning with ``HERE'':\\ Local Policy Generation (in Near Linear Time)}

  % make the title area
  \maketitle
  \pagestyle{plain}

  \begin{abstract}
 Busy project managers grow impatient with analytcs
  \end{abstract}
  \begin{IEEEkeywords}
    defect prediction, CART
  \end{IEEEkeywords}

\section{Introduction}

In the $21^{st}$ century, it is now impossible to manually browse all
the available software defect data.  For example, as of April 2015,
Mozilla Firefox has over a million bug reports on software projects.  While it is
now possible to automatically analyze such data with data miners, at
some stage a group of business users will have to convene to {\em
  interpret the results} (e.g., to decide if it is wise to deploy the
results as a defect reduction method within an organization).
These business  users are now demanding that data mining tools
be augmented with tools to support  business-level
interpretation of that data. For example,
at a  panel on software analytics at ICSE'12,
industrial practitioners lamented the state of the art in data mining
and software engineering~\cite{menzies12a}. Panelists commented that
``prediction is all well and good, but what about decision
making?''. That is, these panelists are more interested in the interpretations
that follow the mining, rather than just  the mining.

In order to satisfy these panelists, w  explore the generation of {\em policies} in the context
of software analytics. Such {\em policies} are recommendations of what
to change in order to better achieve some goal. In this paper the two
case studies are:
\bi
\item Learning code changes to static code features that reduce
the number of defects;
\item Learning reconfigurations of Makefiles such that, when the code
is compiled, that code runs faster.
\ei
Note that {\em policy generation} is different to the standard
data mining tasks of prediction or classification.  Predictors
and classifiers only tell us what {\em is} while policy 
generators tell us {\em what to do}.

The tool used to generate these policies is ``HERE'', an instance-based
local search algorithm that looks for improvement trends in the data,
then adjusting examples to nudge them along that improvement. While
our case studies are defect and runtime reduction, HERE is a general
purpose algorithm that could be applied to any table of data with at least
one column whose values can be sorted from ``desired'' to ``undesired''.

\section{Related Work}
Policy generation is different to standard data mining in that the 
latter is most concerned with what {\em is} rather than {\em what to do}.
For example, a classification or prediction system such as C4.5~\cite{quinlan92} or CART~\cite{breiman84} can predict for a discrete or continuous class variable
(respectively). As such, they can be used as a sub-routine within a
policy generator. For example, later in this paper we will use the CART
prediction system to assess the policies generated by HERE.

Policy generation with HERE is different to the recommendor systems.
As described by Robillard and Walker~\cite{rob14}, recommendor systems
in software engineering
are less {\em directive} and more    {\em collaborative} than policy
generators:
\bi
\item
Directive systems such as HERE tell developers exactly what to do
(e.g. ``use these settings in a Makefile'') 
\item
Collaborative systems are more suggestive guides that
help (e.g.) programmers focus on very small sets
with  very large libraries of code of documentation.
\ei
Collaborative systems may not presume to know what to do
in that smaller set (while the directive systems would issue an edict
such as  ``change this to that'').

We also distinguish HERE's policy generation fro the multi-objective optimization methods explored by Harman and Krall and Menzies and 
and many ithers.

Previous with have explored model-based policy generation with STAR,
NOVA, and instance-based policy generation with  W2.

refactoring XXX

Finally, we note that HERE is a temporal transfer learner.

{\bf RQ1: Can Instance-based Learning techniques be used to create Planning tools that can better analyse software defect?}

@@

\begin{figure*}[htbp!]
  \renewcommand{\baselinestretch}{0.8}\begin{center}
    {\scriptsize
      \begin{tabular}{c|l|p{4.7in}}
        amc & average method complexity & e.g. number of JAVA byte codes\\\hline
        avg\, cc & average McCabe & average McCabe's cyclomatic complexity seen
        in class\\\hline
        ca & afferent couplings & how many other classes use the specific
        class. \\\hline
class. \\\hline
        cam & cohesion amongst classes & summation of number of different
        types of method parameters in every method divided by a multiplication
        of number of different method parameter types in whole class and
        number of methods. \\\hline
        cbm &coupling between methods &  total number of new/redefined methods
        to which all the inherited methods are coupled\\\hline
        cbo & coupling between objects & increased when the methods of one
        class access services of another.\\\hline
        ce & efferent couplings & how many other classes is used by the
        specific class. \\\hline
        dam & data access & ratio of the number of private (protected)
        attributes to the total number of attributes\\\hline
        dit & depth of inheritance tree &\\\hline
        ic & inheritance coupling &  number of parent classes to which a given
        class is coupled (includes counts of methods and variables inherited)
        \\\hline
        lcom & lack of cohesion in methods &number of pairs of methods that do
        not share a reference to an instance variable.\\\hline
        locm3 & another lack of cohesion measure & if $m,a$ are  the number of
        $methods,attributes$
        in a class number and $\mu(a)$  is the number of methods accessing an
        attribute, 
        then
        $lcom3=((\frac{1}{a} \sum, j^a \mu(a, j)) - m)/ (1-m)$.
        \\\hline
        loc & lines of code &\\\hline
        max\, cc & maximum McCabe & maximum McCabe's cyclomatic complexity seen
        in class\\\hline
        mfa & functional abstraction & number of methods inherited by a class
        plus number of methods accessible by member methods of the
        class\\\hline
        moa &  aggregation &  count of the number of data declarations (class
        fields) whose types are user defined classes\\\hline
        noc &  number of children &\\\hline
        npm & number of public methods & \\\hline
        rfc & response for a class &number of  methods invoked in response to
        a message to the object.\\\hline
        wmc & weighted methods per class &\\\hline
        \rowcolor{lightgray}
        defect & defect & Boolean: where defects found in post-release bug-tracking systems.
      \end{tabular}
    }
  \end{center}
  \caption{OO measures used in our defect data sets.  Last line is
    the dependent attribute (whether a defect is reported to  a
    post-release bug-tracking system).}\label{fig:ck}
\end{figure*}

@@

\begin{figure}[tbp!]
% \subfloat[\label{oracle}]{\includegraphics[width=\linewidth]{{_figs//Oracle}}\\
\includegraphics[width=\linewidth]{_figs/WHAT}
\caption{Experimental Rig}
\label{fig:rig}

%   \subfloat[Experimental Rig for Defect Prediction]{  \includegraphics[width=\linewidth]{_figs/WHAT}
%   \label{fig:rig2}}

@@

\noindent\begin{minipage}{0.5\textwidth}
  {\scriptsize \textbf{Ant}\\}
  {\scriptsize  \begin{tabular}{{l@{~~~~}l@{}r@{~~~~}r@{~~~~}c}}
      \arrayrulecolor{darkgray}
      \rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\\hline
  1 & 0.75 &    -0.63  &  0.08 & \quart{2}{7}{5}{144} \\
  1 & 0.75, weighting &    -0.6  &  0.2 & \quart{0}{16}{8}{144} \\
\hline  2 & 0.5, weighting &    -0.42  &  0.11 & \quart{17}{10}{23}{144} \\
  2 & 0.5 &    -0.42  &  0.11 & \quart{19}{9}{23}{144} \\
  2 & 0.75, weighting, Prune=50\% &    -0.4  &  0.11 & \quart{20}{9}{25}{144} \\
\hline  3 & 0.25 &    -0.28  &  0.09 & \quart{31}{7}{35}{144} \\
  3 & 0.25, weighting &    -0.28  &  0.08 & \quart{31}{7}{35}{144} \\
\hline  4 & 0.5, weighting, Prune=50\% &    -0.25  &  0.06 & \quart{35}{5}{38}{144} \\
\hline  5 & 0.25, weighting, Prune=50\% &    -0.19  &  0.05 & \quart{41}{4}{43}{144} \\
\hline  6 & Baseline &    -0.11  &  0.03 & \quart{47}{2}{49}{144} \\
\hline \end{tabular}}
\end{minipage}
\noindent\begin{minipage}{0.5\textwidth}
  \flushleft
  {\scriptsize \textbf{Camel}\\}
{\scriptsize  \begin{tabular}{{l@{~~~~}l@{}r@{~~~~}r@{~~~~}c}}
\arrayrulecolor{darkgray}
\rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\\hline
  1 &  0.75, weighting, Prune=50\% &    -0.41  &  0.1 & \quart{2}{14}{9}{205} \\
  1 &  0.75 &    -0.41  &  0.23 & \quart{1}{32}{9}{205} \\
  1 &  0.75, weighting &    -0.39  &  0.16 & \quart{0}{22}{12}{205} \\
\hline  2 &  0.5, weighting, Prune=50\% &    -0.27  &  0.09 & \quart{19}{12}{29}{205} \\
  2 &  0.5 &    -0.26  &  0.12 & \quart{20}{17}{30}{205} \\
  2 &  0.5, weighting &    -0.24  &  0.09 & \quart{24}{13}{33}{205} \\
\hline  3 &  0.25, weighting, Prune=50\% &    -0.2  &  0.05 & \quart{36}{7}{38}{205} \\
  3 &  0.25, weighting &    -0.19  &  0.07 & \quart{36}{9}{40}{205} \\
  3 &  0.25 &    -0.17  &  0.06 & \quart{37}{8}{43}{205} \\
\hline  4 &  Baseline &    -0.15  &  0.06 & \quart{41}{8}{45}{205} \\
\hline \end{tabular}}
\end{minipage}

\noindent\begin{minipage}{0.5\textwidth}
  \flushleft
  {\scriptsize \textbf{Ivy}\\[-0.05cm]}
{\scriptsize  \begin{tabular}{{l@{~~~~}l@{}r@{~~~~}r@{~~~~}c}}
\arrayrulecolor{darkgray}
\rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\\hline
  1 &     0.75 &    -0.57  &  0.17 & \quart{0}{16}{6}{163} \\
  1 &   0.75, weighting &    -0.55  &  0.11 & \quart{3}{11}{8}{163} \\
\hline  2 &   0.75, weighting, Prune=50\% &    -0.38  &  0.11 & \quart{19}{11}{25}{163} \\
  2 &    0.5, weighting &    -0.36  &  0.12 & \quart{23}{12}{27}{163} \\
  2 &   0.5 &    -0.33  &  0.11 & \quart{25}{11}{30}{163} \\
\hline  3 &   0.5, weighting, Prune=50\% &    -0.27  &  0.08 & \quart{30}{8}{36}{163} \\
\hline  4 &   0.25, weighting &    -0.2  &  0.07 & \quart{41}{7}{43}{163} \\
  4 &     0.25 &    -0.16  &  0.04 & \quart{43}{4}{47}{163} \\
  4 &     Baseline &    -0.16  &  0.0 & \quart{47}{0}{47}{163} \\
\hline  5 &   0.25, weighting, Prune=50\% &    -0.15  &  0.04 & \quart{45}{4}{48}{163} \\
\hline \end{tabular}}
\end{minipage}
\noindent\begin{minipage}{0.5\textwidth}
  \flushleft
  {\scriptsize \textbf{Jedit}\\}
  {\scriptsize  \begin{tabular}{{l@{~~~~}l@{}r@{~~~~}r@{~~~~}c}}
\arrayrulecolor{darkgray}
\rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\\hline
  1 &  0.75, weighting, Prune=50\% &    -0.41  &  0.18 & \quart{0}{20}{8}{172} \\
  1 &  0.75 &    -0.35  &  0.26 & \quart{0}{30}{15}{172} \\
\hline  2 &  0.75, weighting &    -0.25  &  0.17 & \quart{16}{20}{26}{172} \\
  2 &  0.5, weighting, Prune=50\% &    -0.21  &  0.1 & \quart{23}{11}{31}{172} \\
\hline  3 &   0.5 &    -0.17  &  0.08 & \quart{32}{9}{36}{172} \\
  3 &  0.5, weighting &    -0.14  &  0.09 & \quart{31}{10}{39}{172} \\
\hline  4 &  0.25, weighting, Prune=50\% &    -0.12  &  0.06 & \quart{39}{7}{41}{172} \\
\hline  5 &  0.25 &    -0.08  &  0.05 & \quart{43}{5}{46}{172} \\
  5 &  0.25, weighting &    -0.08  &  0.06 & \quart{43}{6}{46}{172} \\
\hline  6 &  Baseline &    -0.06  &  0.01 & \quart{47}{1}{48}{172} \\
\hline \end{tabular}}
\end{minipage}

\noindent\begin{minipage}{0.5\textwidth}
  \flushleft
  {\scriptsize \textbf{Log4j}\\}
  {\scriptsize  \begin{tabular}{{l@{~~~~}l@{}r@{~~~~}r@{~~~~}c}}
\arrayrulecolor{darkgray}
\rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\\hline
  1 &  0.75, weighting, Prune=50\% &    -0.19  &  0.13 & \quart{0}{28}{15}{273} \\
\hline  2 &  0.75 &    -0.13  &  0.06 & \quart{23}{13}{28}{273} \\
  2 &  0.5, weighting, Prune=50\% &    -0.13  &  0.05 & \quart{23}{11}{28}{273} \\
  2 &  0.75, weighting &    -0.12  &  0.1 & \quart{15}{21}{30}{273} \\
\hline  3 &  0.5, weighting &    -0.1  &  0.03 & \quart{28}{6}{34}{273} \\
\hline  4 &   0.5 &    -0.1  &  0.07 & \quart{28}{15}{34}{273} \\
  4 &  0.25 &    -0.09  &  0.04 & \quart{34}{9}{36}{273} \\
  4 &  0.25, weighting, Prune=50\% &    -0.09  &  0.04 & \quart{34}{9}{36}{273} \\
  4 &  0.25, weighting &    -0.06  &  0.04 & \quart{34}{9}{43}{273} \\
\hline  5 &  Baseline &    -0.06  &  0.03 & \quart{43}{6}{43}{273} \\
\hline \end{tabular}}
\end{minipage}
\noindent\begin{minipage}{0.5\textwidth}
  \flushleft
  {\scriptsize \textbf{Lucene}\\}
  {\scriptsize  \begin{tabular}{{l@{~~~~}l@{}r@{~~~~}r@{~~~~}c}}
\arrayrulecolor{darkgray}
\rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\\hline
  1 &  0.75, weighting &    -0.15  &  0.09 & \quart{0}{29}{9}{393} \\
  1 &  0.75 &    -0.13  &  0.09 & \quart{0}{29}{16}{393} \\
  1 &  0.75, weighting, Prune=50\% &    -0.12  &  0.08 & \quart{6}{27}{19}{393} \\
\hline  2 &  Baseline &    -0.1  &  0.03 & \quart{26}{10}{26}{393} \\
  2 &  0.5, weighting, Prune=50\% &    -0.1  &  0.03 & \quart{23}{10}{26}{393} \\
\hline  3 &  0.5, weighting &    -0.08  &  0.06 & \quart{23}{20}{33}{393} \\
  3 &  0.25, weighting, Prune=50\% &    -0.07  &  0.03 & \quart{33}{10}{36}{393} \\
  3 &  0.5 &    -0.07  &  0.05 & \quart{29}{17}{36}{393} \\
\hline  4 &  0.25, weighting &    -0.04  &  0.04 & \quart{36}{13}{46}{393} \\
  4 &  0.25 &    -0.04  &  0.02 & \quart{39}{7}{46}{393} \\
\hline \end{tabular}}
\end{minipage}

\noindent\begin{minipage}{0.5\textwidth}
  \flushleft
  {\scriptsize \textbf{Poi}\\}
  {\scriptsize  \begin{tabular}{{l@{~~~~}l@{}r@{~~~~}r@{~~~~}c}}
      \arrayrulecolor{darkgray}
\rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\\hline
  1 & 0.75, weighting &    -0.45  &  0.1 & \quart{6}{10}{11}{162} \\
  1 &  0.75 &    -0.44  &  0.23 & \quart{0}{23}{12}{162} \\
\hline  2 & 0.5, weighting &    -0.32  &  0.23 & \quart{12}{24}{24}{162} \\
  2 & 0.5 &    -0.26  &  0.23 & \quart{18}{24}{31}{162} \\
  2 & 0.75, weighting, Prune=50\% &    -0.25  &  0.19 & \quart{17}{20}{32}{162} \\
\hline  3 & 0.5, weighting, Prune=50\% &    -0.19  &  0.09 & \quart{34}{9}{38}{162} \\
  3 &  0.25 &    -0.19  &  0.11 & \quart{32}{11}{38}{162} \\
  3 & 0.25, weighting &    -0.17  &  0.14 & \quart{30}{14}{40}{162} \\
\hline  4 & 0.25, weighting, Prune=50\% &    -0.12  &  0.09 & \quart{40}{9}{45}{162} \\
\hline  5 &  Baseline &    -0.09  &  0.03 & \quart{46}{3}{48}{162} \\
\hline \end{tabular}}
\end{minipage}
\noindent\begin{minipage}{0.5\textwidth}
  \flushleft
  {\scriptsize \textbf{Synapse}\\}
  {\scriptsize  \begin{tabular}{{l@{~~~~}l@{}r@{~~~~}r@{~~~~}c}}
\arrayrulecolor{darkgray}
\rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\\hline
  1 & 0.75, weighting &    -0.56  &  0.2 & \quart{7}{18}{11}{148} \\
  1 & 0.75 &    -0.48  &  0.34 & \quart{0}{29}{18}{148} \\
\hline  2 & 0.5 &    -0.4  &  0.27 & \quart{14}{24}{25}{148} \\
  2 & 0.5, weighting &    -0.37  &  0.17 & \quart{21}{15}{28}{148} \\
\hline  3 & 0.25 &    -0.23  &  0.16 & \quart{31}{14}{40}{148} \\
  3 & 0.25, weighting &    -0.23  &  0.1 & \quart{38}{9}{40}{148} \\
  3 & 0.75, weighting, Prune=50\% &    -0.19  &  0.08 & \quart{40}{7}{43}{148} \\
\hline  4 & 0.25, weighting, Prune=50\% &    -0.17  &  0.08 & \quart{42}{7}{45}{148} \\
  4 & Baseline &    -0.15  &  0.0 & \quart{47}{0}{47}{148} \\
  4 & 0.5, weighting, Prune=50\% &    -0.15  &  0.11 & \quart{40}{9}{47}{148} \\
\hline \end{tabular}}
\end{minipage}
